Review Paper Draft

### 2020-07-20 main.tex
Figures: updating figures to use 1) new simulation data that incorporated a manual intercept, 2) black and white color scheme

\pb{Just FYI, it's hard to tell bias and var apart in black and white} \anna{will fix this, greek letters, labels}

@@

\begin{figure}[H]
    \centering
    \includegraphics[scale = 1]{figures/eta_beta_hat.png}
     \caption{$\bbeta$ and $\eta$ estimation accuracy of LMM-Lasso-Rakitsch and LMM-Lasso-ggmix for varying $\eta$ levels and sample sizes with independent subpopulation data, coarse subpopulation structure, $\xi = 0.8$, and dichotomous-discordant environmental effect structure.}
    \label{fig:eta_beta_mse}
\end{figure}

\begin{figure}[H]
    \centering
    \includegraphics[scale = 0.8]{figures/time_ratio.png}
    \caption{Computing time of LMM-Lasso-Rakitsch compared with that of LMM-Lasso-ggmix for varying sample sizes with independent subpopulation structure, coarse subpopulation structure, $\eta = 0.5$, $\xi = 0.8$, and dichotomous-discordant environmental effect structure.}
    \label{fig:time}
\end{figure}

In addition, we have found that LMM-Lasso-ggmix performs poorly in a low-dimensional setting due to the ill-conditioning of the RRM. Given its intended use for the analysis of high-dimensional data, this fact could be of little consequence to practitioners. However, although its estimation accuracy in high dimensions is on par with that of LMM-Lasso-Rakitsch, as shown in figure \ref{fig:eta_beta_mse}, this is also a setting in which the computational time required may be prohibitive for practical applications. Figure \ref{fig:time} shows the ratio of computing time required for LMM-Lasso-ggmix compared to that of LMM-Lasso-Rakitsch, for various sample sizes. The horizontal dashed line at 1 indicates both methods require the same computing time. Despite its comparable performance in accurately estimating $\hat{\bbeta}$, LMM-Lasso-ggmix takes requires as much as 75 times the computing time of LMM-Lasso-Rakitsch. Thus, LMM-Lasso-Rakitsch seems to be a more attractive and scalable method than LMM-Lasso-ggmix.

@@

Finally, we considered two implementations of the LMM-Lasso method: LMM-Lasso-Rakitsch and LMM-Lasso-ggmix, which differ in their variance estimation procedures and computational implementations. Although we found that both methods perform similarly in terms of $\bbeta$ estimation accuracy, LMM-Lasso-ggmix has several drawbacks. Firstly, it suffers from instability in low dimensions. Secondly, although LMM-Lasso-Rakitsch and LMM-Lasso-ggmix perform comparably in high dimensions, LMM-Lasso-ggmix requires as much as \anna{75 - check} times the computing time of LMM-Lasso-Rakitsch due to its iterative estimation procedure. Thirdly, while the additional time required of LMM-Lasso-ggmix may be worthwhile if it yielded more accurate estimates of $\eta$, or narrow-sense heritability, we have been unable to identify a scenario where its narrow-sense heritability estimates are greatly superior to those of LMM-Lasso-Rakitsch. We have implemented the LMM-Lasso-Rakitsch method using the equivalent, but more interpretable, $\eta$ paramaterization in the \texttt{R} package, \texttt{penalizedLMM (final name tbd)}, available on the author's github page: \url{https://github.com/areisett/penalizedLMM}.

>>>>

@@

\begin{figure}[H]
    \centering
    \includegraphics[scale = 1]{figures/eta_beta_hat.png}
     \caption{$\bbeta$ and $\eta$ estimation accuracy of LMM-Lasso-Rakitsch and LMM-Lasso-ggmix for varying $\eta$ levels and sample sizes with independent subpopulation data, coarse subpopulation structure, $\xi = 0.8$, and dichotomous-discordant environmental effect structure.}
    \label{fig:eta_beta_mse}
\end{figure}
\anna{beta-hat and eta-hat seems like a bug with ggplot2 update (?) - checking on this}

\begin{figure}[H]
    \centering
    \includegraphics[scale = 0.8]{figures/time_ratio.png}
    \caption{Computing time of LMM-Lasso-Rakitsch compared with that of LMM-Lasso-ggmix for varying sample sizes with independent subpopulation structure, coarse subpopulation structure, $\eta = 0.5$, $\xi = 0.8$, and dichotomous-discordant environmental effect structure.}
    \label{fig:time}
\end{figure}
\anna{Note figure \ref{fig:time} is on raw scale, not log10. This is because the negative values on the error bars create problems and become NaN on the log10 scale}

\begin{figure}[H]
    \centering
    \includegraphics[scale = 0.8]{figures/time_ratio_box.png}
    \caption{\anna{Alternate time fig} Computing time of LMM-Lasso-Rakitsch compared with that of LMM-Lasso-ggmix for varying sample sizes with independent subpopulation structure, coarse subpopulation structure, $\eta = 0.5$, $\xi = 0.8$, and dichotomous-discordant environmental effect structure.}
    \label{fig:time_box}
\end{figure}

In addition, we have found that LMM-Lasso-ggmix performs poorly in a low-dimensional setting due to the ill-conditioning of the RRM. Given its intended use for the analysis of high-dimensional data, this fact could be of little consequence to practitioners. However, although its estimation accuracy in high dimensions is on par with that of LMM-Lasso-Rakitsch, as shown in figure \ref{fig:eta_beta_mse}, this is also a setting in which the computational time required may be prohibitive for practical applications. Figure \ref{fig:time} shows the ratio of computing time required for LMM-Lasso-ggmix compared to that of LMM-Lasso-Rakitsch, for various sample sizes. The horizontal dashed line at 1 indicates both methods require the same computing time. Despite its comparable performance in accurately estimating $\hat{\bbeta}$, LMM-Lasso-ggmix takes requires an average of \anna{73.4} times the computing time of LMM-Lasso-Rakitsch. Thus, LMM-Lasso-Rakitsch seems to be a more attractive and scalable method than LMM-Lasso-ggmix.

@@

Finally, we considered two implementations of the LMM-Lasso method: LMM-Lasso-Rakitsch and LMM-Lasso-ggmix, which differ in their variance estimation procedures and computational implementations. Although we found that both methods perform similarly in terms of $\bbeta$ estimation accuracy, LMM-Lasso-ggmix has several drawbacks. Firstly, it suffers from instability in low dimensions. Secondly, although LMM-Lasso-Rakitsch and LMM-Lasso-ggmix perform comparably in high dimensions, LMM-Lasso-ggmix requires an average of 73.4 and as much as 167.57 \anna{73.4 is the mean ratio + sd, but the max absolute ratio is 167.57 - which should I report?} times the computing time of LMM-Lasso-Rakitsch due to its iterative estimation procedure. Thirdly, while the additional time required of LMM-Lasso-ggmix may be worthwhile if it yielded more accurate estimates of $\eta$, or narrow-sense heritability, we have been unable to identify a scenario where its narrow-sense heritability estimates are greatly superior to those of LMM-Lasso-Rakitsch. We have implemented the LMM-Lasso-Rakitsch method using the equivalent, but more interpretable, $\eta$ paramaterization in the \texttt{R} package, \texttt{penalizedLMM (final name tbd)}, available on the author's github page: \url{https://github.com/areisett/penalizedLMM}.
